Concurrent and Distributed Programming in Harmony

### 2022-01-13 paper/paper.tex
Minor improvement
Added missing citation

The Harmony distribution comes with a collection of specifications,
each often with multiple implementations.  The lock specification
comes with the spinlock implementation of \autoref{fig:synch}(a), but
also a ticket lock implementation and one based on continuations and
a ready queue.  There are various concurrent queue implementations,
including the lock-free implementation of~\cite{MS96}.

@@

There are three sources of nondetermism in Harmony: \texttt{Choose}
operations, thread interleaving, and interrupts.
When it comes to interleaving, an important observation is that
local operations on the state of a context (updates to its program
counter, local variables, or stack) are not visible to other threads.
An important optimization that significantly
reduces the size of the set of generated states is to treat a
sequence of operations as atomic if only its first operation is an
operation that accesses the shared state (\texttt{Load}, \texttt{Store},
\texttt{Del}, or \texttt{Stop}) or a \texttt{Choose} or \texttt{Print}
operation.  We call such operations \emph{breakable}.
Note that this is essentially a form of Partial Order Reduction~\cite{}.

>>>>

The Harmony distribution comes with a collection of specifications,
each often with multiple implementations.  The lock specification
comes with the spinlock implementation of \autoref{fig:synch}(a), but
also a ticket lock implementation and one based on continuations and
a ready queue.  The distribution also includes various concurrent
queue implementations, including the lock-free implementation
of~\cite{MS96}.

@@

There are three sources of nondetermism in Harmony: \texttt{Choose}
operations, thread interleaving, and interrupts.
When it comes to interleaving, an important observation is that
local operations on the state of a context (updates to its program
counter, local variables, or stack) are not visible to other threads.
An important optimization that significantly
reduces the size of the set of generated states is to treat a
sequence of operations as atomic if only its first operation is an
operation that accesses the shared state (\texttt{Load}, \texttt{Store},
\texttt{Del}, or \texttt{Stop}) or a \texttt{Choose} or \texttt{Print}
operation.  We call such operations \emph{breakable}.
Note that this is essentially a form of Partial Order Reduction~\cite{Val91}.
